Query Optimization for Dynamic Imputation

### 2017-03-01 paper/main.tex
Update plan time results
paper: add affiliations
paper: revise abstract

\author{
  Jos\'e Cambronero\thanks{Author contributed equally to this paper.} \\
  \texttt{jcamsan@csail.mit.edu}
  \and
  John K. Feser\footnotemark[1] \\
  \texttt{feser@csail.mit.edu}
  \and
  Micah J. Smith\footnotemark[1] \\
  \texttt{micahs@mit.edu}
  \and
  Samuel Madden \\
  \texttt{madden@csail.mit.edu}}

@@

\begin{abstract}
Missing values abound in data analysis and often present a serious challenge for the usability of data. Users
are forced to pick between removing tuples with missing values or creating a clean duplicate of their data
by applying a potentially-expensive imputation strategy. Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, 
performing any operations needed on the fly
for each query. This allows users to immediately explore
their data, while the system picks the optimal placement of imputation operations. This placement is based
on the specific query issued and a user-provided parameter that trades off data
quality and runtime performance. We incorporate the imputation operators into the relational algebra, allowing
for traditional optimizations to take place. Our experiments evaluate this approach on two real-world survey-based datasets
from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}. Our
results show that the optimizer generates query plans that execute between \lowxalphazero{}
and \highxalphazeroexacs{} times as fast as imputing at the base tables and then executing
queries, making exploratory data analysis using our system feasible.  Furthermore, we show
that the query results from on-the-fly imputation have
error between \lowsmapealphazero{} and
\highsmapealphaoneexacs{} percent when compared to standard full-table imputation
approach.

\end{abstract}

>>>>

\author{
  Jos\'e Cambronero\thanks{Author contributed equally to this paper.} \\
  MIT CSAIL \\
  \texttt{jcamsan@csail.mit.edu}
  \and
  John K. Feser\footnotemark[1] \\
  MIT CSAIL \\
  \texttt{feser@csail.mit.edu}
  \and
  Micah J. Smith\footnotemark[1] \\
  MIT LIDS \\
  \texttt{micahs@mit.edu}
  \and
  Samuel Madden \\
  MIT CSAIL \\
  \texttt{madden@csail.mit.edu}}

@@

\begin{abstract}
  Missing values abound in data analysis and present a usability challenge.
  Users are forced to pick between removing tuples with missing values or creating a clean duplicate of their data by applying a relatively expensive imputation strategy.
  Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, performing necessary imputations on the fly for each query.
  This allows users to immediately explore their data, while the system picks the optimal placement of imputation operations.
  % This placement is based on the specific query issued and a user-provided parameter that trades off data quality and runtime performance.
  % We incorporate the imputation operators into the relational algebra, allowing for traditional optimizations to take place.
  We  evaluate this approach on two real-world survey-based datasets and 
  % from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}.
  our experiments show that our query plans are between \lowxalphazero{} and \highxalphazeroexacs{} times faster than first imputing the base tables.
  Furthermore, we show that the query results from on-the-fly imputation differ in one error measure from the standard full-table imputation approach by \lowsmapealphazero{}--\highsmapealphaoneexacs{}\%.
  Finally, we show that while dropping tuples with missing values that fail query constraints discards 3--88\% of the data, on-the-fly imputation loses only 0--10\%.
\end{abstract}
